\thetitle

### 2010-01-22 doc/paper.tex
doc: Fix monad citation.
Ignore-this: 53ce628e2cccea337ff4760129dcafed

darcs-hash:20100122150926-bab43-89092f3f26e5c45021656a68a7077b6cbe8f856d.gz

One practical way to answer the question of how such a doubly negated proposition might be used to prove things is to observe that double negation, as a function on types/propositions, is a monad \cite{bla}. Writing |DN P| for |~ ~ P|, we have the following two key operations that make |DN| a monad:

>>>>

One practical way to answer the question of how such a doubly negated proposition might be used to prove things is to observe that double negation, as a function on types/propositions, is a monad \cite{wadler95monads}. Writing |DN P| for |~ ~ P|, we have the following two key operations that make |DN| a monad:
